Measurement Bias from Address Aliasing

### 2014-05-25 paper.tex
Added related work section

>>>>

\section{Related Work}
\label{sec:related}
Measurement bias and observer effect in performance analysis has been studied in detail by Mytkowicz et al~\shortcite{Mytkowicz:2008:OE&MB,Mytkowicz:2008:Easy}.
The authors introduce environment variables and link ordering as examples of external bias triggers, showing how standardised {\small SPECint} benchmarks suffer from measurement bias when trying to evaluate the effectiveness of O3 over O2. 
Strategies for detecting bias through causal analysis and randomization of experimental setups is introduced.
The microkernel example we analyzed is taken from a followup paper by the same authors, presenting similar results for an older Core 2 processor~\cite{Mytkowicz:2009:WrongData}.
Assuming the root causes of measurement bias were the same, our results indicate that address aliasing issues is probably relevant on several previous generations of Intel architectures as well.

Techniques for ``Blind'' optimization using search over variant spaces, is introduced by \citeN{Knights:2009:BlindOpt}.
Their space of variants consist of different position and alignments for each function and global variable, in principle exploring the different configurations possible by altering link order.
The authors of MAO present a framework for extending compilers to provide very low level microarchitectural assembly optimization~\cite{Hundt:2011:MAO}.
Different techniques are used, including rules, pattern matching, and random insertion of nop-instructions.
